DTOADQ

### 2017-12-04 testdocs/test.tex
'finished' BDPT got transmittive to work

\begin{document}
  \maketitle
  \section{Introduction}

  \section{Signed Distance Fields}
  Signed Distance Fields (SDFs) are a mathematical tool to represent a 3D
primitive by describing its surface via a distance field. Given an arbitrary
point in space, the SDF of a primitive is the distance to its nearest
point/surface. For example, the SDF of a sphere is $\Vert\:O\:\Vert - R$. With
SDFs, it's possible to march a ray along the scene until it hits the surface of
an SDF within a given bound, using the returned SDF distance as the distance to
march. Some example SDFs are shown below: \begin{align*}
  S(P, R) &= \Vert\:P\:\Vert - R & \text{Sphere with Radius}\\
  S(P, N) &= P \cdot N  & \text{Plane with Normal}\\
  S(P, H, R) &= <\Vert\:P_{x, z}\:\Vert - R, \: P_{y}> - H & \text{Torus with Radius and Hole}\\
  \end{align*}

@@

  This is a larger problem in Light Transport than it is in raytracing because
small discontinuities can impact the lighting of an entire scene. And to add to
that, most interesting operations (such as the meta balls shown in the image
above) will violate Lipschitz. The easiest way to fix this is to multiply the
distance field by a constant to stay below 1, but this is less of a fix and more
of a hack.

@@

The amount that each path contributes differ greatly, so naively weighing
each contribution uniformly by something like 1.0f, or even, by inverse path
length, will producy very noisy images, and would not be worth the additional
computation time that BDPT requires. Thus, as mentioned earlier, probability
distributions of the entire path are taken into account in order to generate
multiple importance samples.
    The formula for multiple importance sampling on BDPT is as so:
  \begin{align}
    MIS_{st}(\bar{x}) = \frac{P_s(\bar{x})}{\Sigma_i{P_i(\bar{x})}} 
  \end{align}
    Conceptually, the numerator $P_s(\bar{x})$ is the path density that was
generated, while the denominator is the path density of other connection
strategies that could could have, in theory, created the path. The
straight forward implementation of this has a lot of problems gone unresolved in
Veach's thesis; PBR 3rd Ed, chapter 16 pg 1014-1016 addresses and describe these
problems. Primarily, $P_i(\bar{x})$ will overflow CLFloat (due to the distance
in the Geometric term), and the straight forward implementation is very long,
hard to debug, and has a poor time complexity. But the important part is the end
result of their solution:
  \begin{align}
    r_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = s,\\
      \frac{\overleftarrow{P}(\bar{x_i})}{\overrightarrow{P}(\bar{x_i})} *
      r_{i+1}(\bar{x}), & i < s,\\
      \frac{\overrightarrow{P}(\bar{x_{i-1}})}{\overleftarrow{P}(\bar{x_{i-1}})}
      * r_{i-1}(\bar{x}), & i > s
    \end{cases}
  \end{align}
    However, DTOADQ can simplify a bit further; unlike above, there are two
paths for which to evaluate. Specifically, in the above term, for where $i < s$,
we have $\frac{\overleftarrow{p}(\bar{x}_i)}{\overrightarrow{p}(\bar{x}_i)}$,
which is the light path (i is iterating towards light-length s). The eye
contribution is inversed from this, (also iterating towards s, hence why
$\bar{x}_{i-1}$ is used). . In DTOADQ's case, the weights are calculated in the
same direction relative to its originator; in this case the perspective of the
eye path. Not only this, but unlike any implementation I've found of BDPT, I
don't recalculate each path's probability and MIS every vertex. That is, usually
on calculating MIS for each connection, the MIS and probability values are
recalculated for each vertex in the path. As this is not possible given that
only the light-path exists in memory, an array for MIS/probability is stored
corresponding to each light vertex, and a single MIS/probability is stored
corresponding to $E_1$. Thus, the weight on each path looks like:
  \begin{align}
    \mathcal{W}_i(\bar{x}) \equiv r_i(\bar{x})\\
    \mathcal{W}_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = 0,\\
      \frac{\overleftarrow{p_i}(\bar{x_i})}{\overrightarrow{p_i}(\bar{x_i})} *
      \mathcal{W}_{i-1}(\bar{x}), & i > 0
    \end{cases}
  \end{align}
    And then the expanded form of $\mathcal{W}_i(\bar{x})$ looks like
  \begin{align}
    \mathcal{W}_i(\bar{x}) = \Pi_{n=2}^i(\frac{\overleftarrow
    {p_{\sigma}}(x_n)\overleftarrow {G}(x_n)}
    {\overrightarrow{p_{\sigma}}(x_n)\overrightarrow{G}(x_n)})
    * \frac{\overleftarrow{p_A}(x_1)}{\overrightarrow{p_A}(x_1)}
  \end{align}
    And now the MIS looks like:
  \begin{align}
    MIS_{s, t}(\bar{y}, \bar{z}) =
    \frac{1.0f}{\mathcal{W}_s(\bar{y}) + \mathcal{W}_t(\bar{z}) + 1.0f}
  \end{align}
    Thus, the final rendering equation for DTOADQ looks like such:
  \begin{align}
    P = \frac{1.0f}{N} \Sigma_{0}^{N} \Sigma_{s \le 0} \Sigma_{t \le 0}
    \alpha^L_s c_{s,t} \alpha^E_t MIS_{s, t}(\bar{y}, \bar{z})
  \end{align}

  \begin{align}
    P_i(\bar{x}_{s, t}) = P^L_s p^E_t
  \end{align}

  \begin{align}
    p^{L|E}_i(\bar{x}) =
    \begin{cases}
      1.0f, & i = 0,\\
      P_A(x_i), & i = 1,\\
      P_{\sigma}(x_{i-1} \rightarrow x_i) G(x_{i-1} \leftrightarrow x_i)
      P^{L|E}_{i-1}, & i > 1
    \end{cases}
  \end{align}

>>>>

\begin{document}
  \maketitle
  \section{Signed Distance Fields}
  Signed Distance Fields (SDFs) are a mathematical tool to represent a 3D
primitive by describing its surface via a distance field. Given an arbitrary
point in space, the SDF of a primitive is the distance to its nearest
point/surface. For example, the SDF of a sphere is $\Vert\:O\:\Vert - R$. With
SDFs, it's possible to march a ray along the scene until it hits the surface of
an SDF within a given bound, using the returned SDF distance as the distance to
march. Some example SDFs are shown below: \begin{align*}
  S(P, R) &= \Vert\:P\:\Vert - R & \text{Sphere with Radius}\\
  S(P, N) &= P \cdot N  & \text{Plane with Normal}\\
  S(P, H, R) &= <\Vert\:P_{x, z}\:\Vert - R, \: P_{y}> - H & \text{Torus with Radius and Hole}\\
  \end{align*}

@@

  This is a larger problem in light transport than it is in raytracing because
small discontinuities can impact the lighting of an entire scene. And to add to
that, most interesting operations (such as the meta balls shown in the image
above) will violate Lipschitz. The easiest way to fix this is to multiply the
distance field by a constant to stay below 1, but this is less of a fix and more
of a hack.

@@

The amount that each path contributes differ greatly, so naively weighing
each contribution uniformly by something like 1.0f, or even, by inverse path
length, will producy very noisy images, and would not be worth the additional
computation time that BDPT requires. Thus, as mentioned earlier, probability
distributions of the entire path are taken into account in order to generate
multiple importance samples.
    The formula for multiple importance sampling on BDPT is as so:
  \begin{align}
    MIS_{st}(\bar{x}) = \frac{P_s(\bar{x})}{\Sigma_i{P_i(\bar{x})}} 
  \end{align}
    Conceptually, the numerator $P_s(\bar{x})$ is the path density that was
generated, while the denominator is the path density of other connection
strategies that could could have, in theory, created the path. The
straight forward implementation of this has a lot of problems gone unresolved in
Veach's thesis; PBR 3rd Ed, chapter 16 pg 1014-1016 addresses and describe these
problems. Primarily, $P_i(\bar{x})$ will overflow CLFloat (due to the distance
in the Geometric term), and the straight forward implementation is very long,
hard to debug, and has a poor time complexity. But the important part is the end
result of their solution:
  \begin{align}
    r_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = s,\\
      \frac{\overleftarrow{P}(\bar{x_i})}{\overrightarrow{P}(\bar{x_i})} *
      r_{i+1}(\bar{x}), & i < s,\\
      \frac{\overrightarrow{P}(\bar{x_{i-1}})}{\overleftarrow{P}(\bar{x_{i-1}})}
      * r_{i-1}(\bar{x}), & i > s
    \end{cases}
  \end{align}
    However, DTOADQ can simplify a bit further; unlike above, there are two
paths for which to evaluate. Specifically, in the above term, for where $i < s$,
we have $\frac{\overleftarrow{p}(\bar{x}_i)}{\overrightarrow{p}(\bar{x}_i)}$,
which is the light path (i is iterating towards light-length s). The eye
contribution is inversed from this, (also iterating towards s, hence why
$\bar{x}_{i-1}$ is used). . In DTOADQ's case, the weights are calculated in the
same direction relative to its originator; in this case the perspective of the
eye path. Not only this, but unlike any implementation I've found of BDPT, I
don't recalculate each path's probability and MIS every vertex. That is, usually
on calculating MIS for each connection, the MIS and probability values are
recalculated for each vertex in the path. As this is not possible given that
only the light-path exists in memory, an array for sum/probability is stored
corresponding to each light vertex, and a single sum/probability is stored
corresponding to $E_1$. Thus, the weight on each path looks like:
  \begin{align}
    \mathcal{W}_i(\bar{x}) \equiv r_i(\bar{x})\\
    \mathcal{W}_i (\bar{x}) = 
    \begin{cases}
      1.0f, & i = 0,\\
      \frac{\overleftarrow{p_i}(\bar{x_i})}{\overrightarrow{p_i}(\bar{x_i})} *
      \mathcal{W}_{i-1}(\bar{x}), & i > 0
    \end{cases}
  \end{align}
    And now the MIS looks like:
  \begin{align}
    MIS_{s, t}(\bar{y}, \bar{z}) =
    \frac{1.0f}{\mathcal{W}_s(\bar{y}) + \mathcal{W}_t(\bar{z}) + 1.0f}
  \end{align}
